\documentclass[12pt,twoside]{article}

\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
%\usepackage{palatino,lettrine}
\usepackage{fancyhdr}
\usepackage{epsfig}
\usepackage[round,comma,sort]{natbib}
\usepackage{simplemargins}
\usepackage{setspace}
\usepackage{supertabular}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage[margin=1.5cm]{caption}



\newcommand{\profs}{Prof. Jeffrey Varner}
\newcommand{\subj}{1120}

\newlength{\toppush}
\setlength{\toppush}{2\headheight}
\addtolength{\toppush}{\headsep}

\newcommand{\htitle}[3]{\noindent\vspace*{-\toppush}\newline\parbox{6.5in}
{\textit{Introduction to Chemical Engineering: ENGRI 1120}\hfill\newline
Chemical and Biomolecular Engineering, Cornell University \hfill #3\newline
%\profs\hfill Handout #1\vspace*{-.5ex}\newline
\mbox{}\hrulefill\mbox{}}\vspace*{1ex}\mbox{}\newline
\begin{center}{\Large\bf #2}\end{center}}

\newcommand{\handout}[3]{\thispagestyle{empty}
 \markboth{ENGRI 1120 #2}{ENGRI 1120 #2}
 \pagestyle{myheadings}\htitle{#1}{#2}{#3}}

%\setlength{\oddsidemargin}{0pt}
%\setlength{\evensidemargin}{0pt}
%\setlength{\textwidth}{6.5in}
%\setlength{\topmargin}{0in}
%\setlength{\textheight}{8.5in}

%\doublespace
\onehalfspace
\setallmargins{1in}

\renewcommand{\rmdefault}{phv}\renewcommand{\sfdefault}{phv}
\captionsetup[figure]{font=small,labelfont=small}

\begin{document}


\handout{1}{PRELIM 1}{F2022}
\setlength{\parindent}{0pt}

% \newcommand{\solution}{
%   \medskip
%   {\bf Solution:}
% }

\medskip
\hrulefill
\medskip

\vspace{0.25in}

VERSION: DELTA-2

\vspace{0.25in}

NAME:

\vspace{0.25in}

\medskip
\hrulefill
\medskip

\begin{enumerate}

  \item{Prelim 1 has \textit{two} problems and is worth a total of 50 points.}
  \item{You may use your course notes (on the computer, iPad, etc., or paper) or other course materials, e.g., discussion problems, to formulate your solutions.}
  \item{Do not consult with any other person regarding the prelim (except the TAs or JV),
  or use \textit{any form of electronic communication} to discuss the prelim questions.
  Violation of this policy will result in a ZERO for the prelim.}
  \item{Do not consult the interwebs to search for the prelim questions/solutions.
  Violation of this policy will result in a ZERO for the prelim.}
  \item{Show your work and state all assumptions or simplifications.}
  \item{Good luck!}

\end{enumerate}

\medskip
\hrulefill
\medskip



\begin{enumerate}


% Question 2 ===================== %
\clearpage
\include{Reactor}
% ================================ %

% Question 3 ===================== %
\clearpage
\include{ORC}
% ================================ %


% Question 4 ===================== %
% \clearpage
% \include{Q1_v1}
% ================================ %

% Extra -
\clearpage

\end{enumerate}

\end{document}
